Galaxy Zoo: Classifications for Galaxies in HST Legacy Imaging

### 2014-03-04 writeup/gz_hubble_data.tex
Added fake results figure to paper
Shows the current fake results figure from v1/ of the FERENGI analysis.
Warning: FAKE.
Added example ferengi images

%\begin{figure}
%\includegraphics[width=84mm]{barfraction_gasfraction.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
%\caption{The Hubble Sequence illustrated by the examples suggested by Hubble (1926) with images from the SDSS.  The galaxies are: : E0 Ð NGC 3379; E5 Ð NGC 4621;  Sa - NGC 4594 (``The Sombrero");  Sb - NGC 2841; Sc -  NGC 5447 (``The Pinwheel"); SBa - NGC 2859; SBb - NGC 3351 (or M95); SBc - 7479. We have also included an S0 (NGC 6278), not in HubbleÕs original scheme.) \label{sequence}}
%\end{figure}

@@

\section{Redshift Dependent Classification Bias}

@@

@@

An example redshifted image is shown in Figure \ref{exampleFERENGI}.

>>>>

@@

\section{Correcting for Redshift Dependent Classification Bias}

@@

%-----------------------------------------------------------------------------------------------------------------------------------
\begin{figure}
\begin{center}

\includegraphics[width=0.49\textwidth]{fake_results.pdf}

\caption{Fake results of the FERENGI redshifting exercise. For three vote fraction levels and thee surface-brightness levels each, we show the evolution of the 7 evolutionary corrections used with redshift.}

\label{fig:ferengi_results_fake}

\end{center}
\end{figure}
%-----------------------------------------------------------------------------------------------------------------------------------

@@

Two series of example redshifted images are shown in Figure \ref{exampleFERENGI}.

\begin{figure*}
\includegraphics[width=84mm]{example_ferengi.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. \label{exampleFERENGI}}
\end{figure*}
